---
title: "FARSPackage"
author: P.G.
date: "2019-12-22"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FARSPackage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The FARS package contains data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS) for the years 2013, 2014 and 2015. FARS is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

The path of the data for the year 2015 for instance is given by \code{system.file("extdata", "accident_2015.csv.bz2", package ="FARSPackage")}.

The package contains two functions, one to summarize the data for a given year or a range of years and the other to print the locations of fatal injuries for a certain state in a speciafied year.

Let's have a look at the function called \code{fars_summarize_years()}. The example shows the summary of FARS data for the years 2014 and 2015:

```{r}
library(FARSPackage)
fars_summarize_years(2014:2015)
```

Let's have a look at the other function called \code{fars_map_state()}. This function plots a map for fatal injuries in state number 5 for the year 2015:

```{r}
fars_map_state(5,2015)
```
